\section{Construction}

\begin{lemma}
    \label{lem:chooseWf}
    Let \( \alpha \) and \( \beta \) be types, and let \( \alpha \) be well-ordered.
    Let \( d : \alpha \to \symsf{Set}\ \beta \) assign to each \( x : \alpha \) a set of \emph{denied sets}.
    Suppose that for each \( x : \alpha \), we have
    \[ \#\{ y : \alpha \mid y < x \} + \#(d\ x) < \#\beta \]
    Then \clem{Fuzz/Construction}{chooseWf}{there is} an injective function \( f : \alpha \to \beta \) with the property that for each \( x : \alpha \), \( f\ x \not\in d\ x \).
\end{lemma}
\begin{proof}
    For a given \( x : \alpha \), if we have already constructed \( f\ y \) for \( y < x \), we can pick a value for \( f\ x \) not in \( d\ x \) or equal to any \( f\ y \), as
    \begin{align*}
        \#(f '' \{ y : \alpha \mid y < x \} \cup d\ x) &\leq \#(f '' \{ y : \alpha \mid y < x \}) + \#(d\ x) \\
        &\leq \#\{ y : \alpha \mid y < x \} + \#(d\ x) \\
        &< \#\beta
    \end{align*}
    We have thus constructed \( f : \alpha \to \beta \) satisfying the property that \( f\ x \not\in d\ x \).
    For injectivity, suppose \( x \neq y : \alpha \).
    Then either \( x < y \) or \( y < x \); assume the latter without loss of generality.
    The construction of \( f\ x \) was done under the constraint \( f\ x \neq f\ z \) for each \( z < x \), giving the result as required.
\end{proof}
Let \( \beta : \lambda^\bot \) and \( \gamma : \lambda \) with \( \beta \neq \gamma \).
Let \( \beta \) and \( \gamma \) have tangle data and positioned tangles.
Let \( \gamma \) have typed objects.
\begin{definition}
    \label{def:fuzz_deny}
    Construct the function \( d : \tau_\beta \to \symsf{Set}\ \mu \) by
    \begin{align*}
        \nu \in d\ t &\Leftrightarrow (\exists N : \mathcal N,\, N^\circ = \langle \nu, \beta, \gamma \rangle \wedge n\ (\symsf{typed}^N_\gamma\ N) \leq n\ t) \\
        &\quad\vee (\beta = \bot \wedge n\ (\symsf{typed}^N_\gamma\ (\symsf{NL}\ \langle \nu, \bot, \gamma \rangle)) \leq n\ t)
    \end{align*}
\end{definition}
\begin{lemma}
    \label{lem:mk_invImage_lt_le}
    Let \( t : \tau_\beta \).
    Then
    \begin{enumerate}
        \item \( \#\{ t' : \tau_\beta \mid t' < t \} < \#\mu \);
        \item \( \#\{ t' : \tau_\gamma \mid n\ t' \leq n\ t \} < \#\mu \).
    \end{enumerate}
\end{lemma}
\begin{proof}
    Both proofs follow the same strategy.
    First, we use \cref{lem:card_Iio_lt} to reduce to showing that
    \[ \#\{ t' : \tau_\beta \mid t' < t \} \leq \#\{ \nu : \mu \mid \nu < n\ t \} \]
    and
    \[ \#\{ t' : \tau_\gamma \mid n\ t' < n\ t \} \leq \#\{ \nu : \mu \mid \nu \leq n\ t \} \]
    These inequalities of cardinals can be easily shown by proving that the injection \( n \) has the correct codomain in each case.
\end{proof}
\begin{lemma}
    \label{lem:mk_fuzz_deny}
    Let \( t : \tau_\beta \).
    Then \( \#\{ t' : \tau_\beta \mid t' < t \} + \#(d\ t) < \#\mu \).
\end{lemma}
\begin{proof}
    By \cref{lem:mk_invImage_lt_le}(i), it suffices to show \( \#(d\ t) < \#\mu \).
    We show that there are less than \( \mu \) positions that satisfy each of the two conditions in \cref{def:fuzz_deny}.

    For the first condition, we must show that
    \[ \#\{ \nu : \mu \mid \exists N : \mathcal N,\, N^\circ = \langle \nu, \beta, \gamma \rangle \wedge n\ (\symsf{typed}^N_\gamma\ N) \leq n\ t \} < \#\mu \]
    By \cref{lem:mk_invImage_lt_le}(ii) it suffices to produce an injection
    \[ \{ \nu : \mu \mid \exists N : \mathcal N,\, N^\circ = \langle \nu, \beta, \gamma \rangle \wedge n\ (\symsf{typed}^N_\gamma\ N) \leq n\ t \} \to \{ t' : \tau_\gamma \mid n\ t' \leq n\ t \} \]
    This injection is given by mapping \( \nu \) to \( \symsf{typed}^N_\gamma\ N \) where \( N \) is chosen such that \( N^\circ = \langle \nu, \beta, \gamma \rangle \) and \( n\ (\symsf{typed}^N_\gamma\ N) \leq n\ t \).
    It can be seen that this is an injection as the typed near-litter map is injective.

    Now suppose \( \beta = \bot \).
    For the second condition, it suffices by \cref{lem:card_Iio_lt} to produce an injection
    \[ \{ \nu : \mu \mid n\ (\symsf{typed}^N_\gamma\ (\symsf{NL}\ \langle \nu, \bot, \gamma \rangle)) \leq n\ t \} \to \{ \nu : \mu \mid \nu \leq n\ t \} \]
    In this case, we map \( \nu \) to \( n\ (\symsf{typed}^N_\gamma\ (\symsf{NL}\ \langle \nu, \bot, \gamma \rangle)) \).
    This is also injective, as required.
\end{proof}
\begin{definition}
    The \cdef{Fuzz/Construction}{fuzz}{\( f \)-map} from \( \beta \) to \( \gamma \) is the function \( f_{\beta,\gamma} : \tau_\beta \to \mathcal L \) defined by
    \[ f_{\beta,\gamma}\ t = \langle g\ t, \beta, \gamma \rangle \]
    where \( g \) is chosen by applying \cref{lem:chooseWf} to \cref{def:fuzz_deny} and \cref{lem:mk_fuzz_deny}.
\end{definition}
\begin{lemma}
    \label{lem:fuzz_congr}
    Suppose \( f_{\beta,\gamma}\ t = f_{\beta',\gamma'}\ t' \).
    Then \( \beta = \beta' \) and \( \gamma = \gamma' \).
\end{lemma}
\begin{proof}
    Apply the second and third projections to \( f_{\beta,\gamma}\ t \) and \( f_{\beta',\gamma'}\ t' \).
\end{proof}
\begin{lemma}
    \( f_{\beta,\gamma} \) is injective.
\end{lemma}
\begin{proof}
    Follows from \cref{lem:chooseWf}.
\end{proof}
\begin{lemma}
    \label{lem:fuzz_pos}
    Let \( N \) be a near-litter with \( N^\circ = f_{\beta,\gamma}\ t \).
    Then \( n\ t < n\ (\symsf{typed}^N_\gamma N) \).
\end{lemma}
\begin{proof}
    Follows from \cref{lem:chooseWf} and \cref{def:fuzz_deny}.
\end{proof}
\begin{lemma}
    \label{lem:pos_atom_lt_fuzz}
    Let \( a \) be an atom.
    Then \( n\ a < n\ (\symsf{typed}^N_\gamma (\symsf{NL}\ (f_{\bot,\gamma}\ a))) \).
\end{lemma}
\begin{proof}
    Follows from \cref{lem:chooseWf} and \cref{def:fuzz_deny}.
\end{proof}
